Monte Carlo Bootstrap: current developments.

### 2019-03-22 draft.tex
added multipoint and expanded Gliozzi review

\[
\begin{aligned}
  S(\{\Delta_i,l_i\})& = \sum_i \log\Det^2\mathcal{M}_i(\{\Delta_i,l_i\};{z_j}_i)\\
\end{aligned}
\]

>>>>

\[
\begin{aligned}
  S(\{\Delta_i,l_i\})& = \sum_i
  \log\Det^2\mathcal{M}_i(\{\Delta_i,l_i\};\{z_j\}_i),
\end{aligned}
\]
where 
$i$ runs over a subset of all the subsets of $\{z_i\}_{i=1}^{N_z}$ containing
exactly $N_{op}+1$ elements.

For $N_z \sim O(400)$, chosen from a normal distribution centered around $z=1/2$
and with $\sigma =1/5$, one obtains similar or better results than with the
cross regularization approach.
